Cover letter for the IJRR submission \\ ``An efficient acyclic contact planner for multiped robots''

### 2016-01-04 body/intro.tex
adding cover letter

Most of the papers that followed the work of \citeauthor{conf/iser/BretlRLKA04} have explored alternative formulations to handle the combinatorial issue. Two main directions have been explored. \textbf{On one hand, local optimization of both the root trajectory \Pa and the contact positions $\mathcal{P}_2$} has been used, to trade the combinatorial of the complete problem for a differential complexity, at the cost of local convergence. A complete example of the potential offered by such approaches was proposed \citep{Mordatch:2012:DCB:2185520.2185539} and successfully applied to a real robot \citep{mordatch2015}. To keep reasonable computation times, the method uses a simplified dynamic model for the avatar. Still, the computation time is far from interactive  (about 1 minute of computation for a sequence of 20 contacts). \citeauthor{DBLP:conf/humanoids/DeitsT14} propose to solve contact planning globally as a mixed integer problem, but only cyclic, bipedal locomotion is considered. 
\citeauthor{dai2014whole} extend the work of \citeauthor{Posa:2014:DMT:2568343.2568352} to discover the short contact sequence for landing motions, but specify
the contacts manually for more complex interactions.
A major drawback of these optimization based approaches is thus that they only offer local convergence when applied to acyclic contact planning.

@@

It thus appears that an integrated optimization-based approach \citep{Mordatch:2012:DCB:2185520.2185539}, able to generate a locally-optimal, complete trajectory within minutes, currently outperforms
existing planners, decoupled or not. However, recent contributions are able to interpolate dynamically-feasible
trajectories between contact configurations \citep{herzog2015trajectory, Park116, Carpentier2016}. \citeauthor{Carpentier2016} are able to achieve this with real-time performances on the real robot.
To generate the input contact configurations, there is a need for an efficient contact planner, able to break the combinatorial to generate discrete contact sequences rapidly. 
Such a planner holds the promise of a complete real-time multi-contact locomotion system.

>>>>

Most of the papers that followed the work of \citeauthor{conf/iser/BretlRLKA04} have explored alternative formulations to handle the combinatorial issue. Two main directions have been explored. \textbf{On one hand, local optimization of both the root trajectory \Pa and the contact positions $\mathcal{P}_2$} has been used, to trade the combinatorial of the complete problem for a differential complexity, at the cost of local convergence. A complete example of the potential offered by such approaches was proposed \citep{Mordatch:2012:DCB:2185520.2185539} and successfully applied to a real robot \citep{mordatch2015}. To keep reasonable computation times, the method uses a simplified dynamic model for the avatar. Still, the computation time is far from interactive  (about 1 minute of computation for a sequence of 20 contacts). \citeauthor{DBLP:conf/humanoids/DeitsT14} propose to solve contact planning globally as a mixed integer problem, but only cyclic, bipedal locomotion is considered. 
\citeauthor{dai2014whole} extend the work of \citeauthor{Posa:2014:DMT:2568343.2568352} to discover the contact sequence for landing motions, but need to specify
the contacts manually for more complex interactions.
A major drawback of these optimization based approaches is thus that they only offer local convergence when applied to acyclic contact planning.

@@

For completeness, we lastly mention a new kind of approach, recently proposed from the computer graphics field \citep{hamalainen_cpbp_2015}. The authors
use black box physics simulators to perform Model Predictive Control for the motion of a humanoid character, and manage to obtain dynamically consistent motions
at interactive frame rates. While this new approach provides an exciting direction of research, currently the resulting motions
look unnatural, and do not seem applicable to real robots.

It thus appears that, regarding robotics applications, an integrated optimization-based approach \citep{Mordatch:2012:DCB:2185520.2185539}, able to generate a locally-optimal, complete trajectory within minutes, currently outperforms existing planners, decoupled or not. However, recent contributions are able to interpolate dynamically-feasible
trajectories between contact configurations \citep{herzog2015trajectory, Park116, Carpentier2016}. \citeauthor{Carpentier2016} are able to achieve this with real-time performances on the real robot.
To generate the input contact configurations, there is a need for an efficient contact planner, able to break the combinatorial to generate discrete contact sequences rapidly. 
Such a planner holds the promise of a complete real-time multi-contact locomotion system.

### 2016-01-04 body/results.tex
adding cover letter

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario. Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dexterous manipulation.

@@

\subsection{Description of the scenarios}
In all the scenarios considered, the formulation of the problem is always the same:
a start and goal root placements are provided as an input of the scenario.
The framework computes the initial contact configuration, and outputs a sequence of contact configurations connecting it to the goal.
In each scenario we detail the parameters chosen: the heuristics, and the constraints on the reachable workspaces (for instance in all the scenarios,
the reachable workspaces of the legs of HRP-2 are always required to intersect with the environment). 
A companion video available at TODO \url{http://youtu.be/LmLAHgGQJGA} (anonymous link) displays the complete contact sequence obtained in all these scenarios.

>>>>

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario. Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dexterous manipulation.

@@

\subsection{Description of the scenarios}
In all the scenarios considered, the formulation of the problem is always the same:
a start and goal root placements are provided as an input of the scenario.
The framework computes the initial contact configuration, and outputs a sequence of contact configurations connecting it to the goal.
In each scenario we detail the parameters chosen: the heuristics, and the constraints on the reachable workspaces (for instance in all the scenarios,
the reachable workspaces of the legs of HRP-2 are always required to intersect with the environment). 
The companion video presents the complete contact sequence obtained in all these scenarios.
